Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
copyedit/elaborate SVM grid search example
Rearranged the param_grid to make it more suggestive of two separate
grids for two kernels.  (I didn't even know this was possible! :)

As an example, the snippet below illustrates how to optimize the
hyper-parameters of an SVM classifier. It maximizes the $F_1$ score of the
classifier through a 10-fold cross-validation scheme.
\begin{pythoncode}
from sklearn.svm import SVC
from sklearn.grid_search import GridSearchCV

param_grid = [
  {"C": [1, 10, 100, 1000], "kernel": ["linear"]},
  {"C": [1, 10, 100, 1000], "gamma": [0.001, 0.0001],
   "kernel": ["rbf"]},
]

clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
y_pred = clf.predict(X_test)
\end{pythoncode}
Note that, in the above example, two distinct hyper-parameter grids are
considered. This is because it only makes sense to search for \texttt{gamma}
when \texttt{kernel} is set to \texttt{"rbf"}.  Additionally, we see that
\texttt{GridSearchCV} has a \texttt{predict} method, like any other classifier.
This is because \texttt{GridSearchCV} and \texttt{RandomizedSearchCV} in fact
delegate the \texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and
\texttt{score} methods to the best estimator, thus mimicking its behavior.

>>>>

As an example, the snippet below illustrates how to find the
hyper-parameter settings of an SVM classifier (SVC)
that maximize its $F_1$ score,
through 10-fold cross-validation on the training set.
\begin{pythoncode}
from sklearn.grid_search import GridSearchCV
from sklearn.svm import SVC

param_grid = [
  {"kernel": ["linear"], "C": [1, 10, 100, 1000]},
  {"kernel": ["rbf"], "C": [1, 10, 100, 1000],
                      "gamma": [0.001, 0.0001]}
]

clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
clf.fit(X_train, y_train)
y_pred = clf.predict(X_test)
\end{pythoncode}
Note that, in the above example, two distinct hyper-parameter grids are
considered. This is because it only makes sense to search for \texttt{gamma}
when \texttt{kernel} is set to \texttt{"rbf"}.
An SVM with a linear kernel will accept a $\gamma$ parameter,
but ignore it, so the grid search would waste time
trying out effectively equivalent parameter settings.
Additionally, we see that
\texttt{GridSearchCV} has a \texttt{predict} method, like any other classifier.
This is because \texttt{GridSearchCV} and \texttt{RandomizedSearchCV} in fact
delegate the \texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and
\texttt{score} methods to the best estimator
(optionally after re-fitting it on the whole training set).
